Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-22 DGMM2025/paper.tex
rework time complexity graph (wip)

    \pgfplotsset{width=13cm}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                x dir=reverse,
                ylabel={Mean distance},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymax=50,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
                };
                \addlegendentry{sphere1}
                \addplot[
                    color=red,
                ] coordinates {
                    (1,8.90781)(0.875,10.2845)(0.75,11.3734)(0.625,12.5062)(0.5,14.0867)(0.375,16.6192)(0.25,19.6747)
                };
                \addlegendentry{goursat}
                \addplot[
                    color=violet,
                ] coordinates {
                    (0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
                };
                \addlegendentry{torus}
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
                };
                \addlegendentry{leopold}
                \addplot[
                    color=yellow!80!black,
                ] coordinates {
                    (0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
                };
                \addlegendentry{rcube}
                \addplot [
                    color=black,
                    thick,
                    domain=0.25:1,
                    samples=100,
                ] {x^(-0.5)};
                \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
            \end{axis}
        \end{tikzpicture}
        \caption{Mean Visibility Distance as a Function of Grid Resolution}
        \label{fig:meanvisibility-gridstep}
    \end{figure}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                x dir=reverse,
                ylabel={Duration (s)},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                    mark=square,
                ]
                coordinates {
                    (1,0.513)(0.875,0.585)(0.75,0.897)(0.625,1.401)(0.5,2.441)(0.375,4.664)(0.25,11.420)
                };
                \addlegendentry{sphere9 radius 10}
                \addplot[
                    color=red,
                    mark=square,
                ]
                coordinates {
                    (1,0.440)(0.875,0.665)(0.75,0.823)(0.625,1.428)(0.5,2.463)(0.375,4.697)(0.25,11.766)
                };
                \addlegendentry{goursat radius 10}
                \addplot[
                    color=red,
                    mark=triangle,
                ]
                coordinates {
                    (1,1.389)(0.875,2.567)(0.75,3.661)(0.625,7.123)(0.5,13.881)(0.375,28.913)(0.25,77.360)
                };
                \addlegendentry{radius 20}
                \addplot[
                    color=red,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,2.172)(0.875,3.747)(0.75,5.565)(0.625,13.180)(0.5,33.088)(0.375,80.584)(0.25,240.546)
                };
                \addlegendentry{radius 30}
                \addplot[
                    color=violet,
                    mark=square,
                ]
                coordinates {
                    (1,0.057)(0.875,0.081)(0.75,0.097)(0.625,0.197)(0.5,0.330)(0.375,0.800)(0.25,2.253)
                };
                \addlegendentry{torus}
                \addplot[
                    color=violet,
                    mark=triangle,
                ]
                coordinates {
                    (1,0.248)(0.875,0.294)(0.75,0.339)(0.625,0.620)(0.5,1.110)(0.375,2.643)(0.25,9.369)
                };
                \addplot[
                    color=violet,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,0.837)(0.875,0.880)(0.75,0.942)(0.625,1.316)(0.5,2.142)(0.375,5.046)(0.25,20.418)
                };
            \end{axis}
        \end{tikzpicture}
        \caption{Computation Time of Visibility as a Function of Grid Resolution}
        \label{fig:meanvisibility-computationComplexity}
    \end{figure}

>>>>

    \pgfplotsset{width=13cm}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                ylabel={Mean distance},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymax=50,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
                };
                \addlegendentry{sphere1}
                \addplot[
                    color=red,
                ] coordinates {
                    (1,8.90781)(0.875,10.2845)(0.75,11.3734)(0.625,12.5062)(0.5,14.0867)(0.375,16.6192)(0.25,19.6747)
                };
                \addlegendentry{goursat}
                \addplot[
                    color=violet,
                ] coordinates {
                    (0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
                };
                \addlegendentry{torus}
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
                };
                \addlegendentry{leopold}
                \addplot[
                    color=yellow!80!black,
                ] coordinates {
                    (0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
                };
                \addlegendentry{rcube}
                \addplot [
                    color=black,
                    thick,
                    domain=0.25:1,
                    samples=100,
                ] {x^(-0.5)};
                \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
            \end{axis}
        \end{tikzpicture}
        \caption{Mean Visibility Distance as a Function of Grid Resolution}
        \label{fig:meanvisibility-gridstep}
    \end{figure}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={\#Pointels},
                ylabel={Computation Time},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    red,
                    only marks,
                    mark=halfcircle,
                    mark options={solid}
                ] table[row sep=crcr] {
                    10624 2246.69\\
                    4968 793.426\\
                    2584 328.535\\
                    1840 190.401\\
                    1176 93.2502\\
                    912 78.7981\\
                    624 56.3769\\
                    28568 10193.5\\
                    12632 4004.92\\
                    7088 2010.63\\
                    4664 1188.73\\
                    3080 755.754\\
                    2408 545.347\\
                    1736 366.541\\
                    24320 11169.1\\
                    10760 4720.44\\
                    6056 2397.79\\
                    3944 1380.38\\
                    2648 874.979\\
                    2000 580.0\\
                    1520 415.373\\
                    8336 3196.55\\
                    3720 1268.46\\
                    2104 639.305\\
                    1336 342.873\\
                    928 177.54\\
                    680 112.142\\
                    520 87.0747\\
                    37592 12335.6\\
                    16712 5582.38\\
                    9512 2976.21\\
                    6056 1731.32\\
                    4088 990.78\\
                    3032 788.507\\
                    2456 548.66\\
                };
                \addlegendentry{radius 10};
                \addplot[
                    MyGreen,
                    only marks,
                    mark=halfcircle,
                    mark options={solid}
                ] table[row sep=crcr] {
                    1000 1000\\
                };
                \addlegendentry{radius 20};
                \addplot[
                    blue,
                    only marks,
                    mark=halfcircle,
                    mark options={solid}
                ] table[row sep=crcr] {
                    10624 18283.5\\
                    4968 4957.93\\
                    2584 2133.36\\
                    1840 1292.53\\
                    1176 922.51\\
                    912 863.731\\
                    624 813.638\\
                    28568 188784.0\\
                    12632 62237.1\\
                    7088 24874.9\\
                    4664 9043.39\\
                    3080 4407.09\\
                    2408 2641.04\\
                    1736 1820.31\\
                    24320 227432.0\\
                    10760 69706.8\\
                    6056 25408.9\\
                    3944 10094.7\\
                    2648 5269.56\\
                    2000 2948.16\\
                    1520 2082.02\\
                    8336 45045.4\\
                    3720 8638.42\\
                    2104 3238.48\\
                    1336 1731.9\\
                    928 1122.69\\
                    680 928.084\\
                    520 890.592\\
                    37592 257981.0\\
                    16712 84729.7\\
                    9512 36298.8\\
                    6056 15640.2\\
                    4088 6662.17\\
                    3032 4431.71\\
                    2456 2621.98\\
                };
                \addlegendentry{radius 30};
            \end{axis}
        \end{tikzpicture}
        \caption{Computation Time of Visibility as a Function of Grid Resolution}
        \label{fig:meanvisibility-computationComplexity}
    \end{figure}
